\thetitle

### 2021-03-01 writing/challenges.tex
re-established the old organization

The {\em first challenge\/} is to find a representative collection of impedance
mismatches. They must represent mistakes that programmers accidentally create
and that the run-time checks of academic systems catch. In other words, the
experiment calls for a collection of type mistakes in mix-typed programs that is
representative of those ``in the wild.''  Unfortunately no such collection
exists, and with good reason. The kind of mistakes needed are typically detected
by unit or integration tests; even if it takes some time to find their sources,
these mistakes do not make it into code repositories with appropriate commit
messages.

@@

The {\em second challenge\/} concerns the differences among the blame assignment
of the three semantic variants.  While Natural assigns blame to {\em one\/}
component, Transient assigns blame to a sequence of components. The Erasure
semantics does not blame a component {\it per se\/}, but it comes with an
exception location and a stack trace, which implicitly suggests parties to
blame.  The different strategies greatly affect the behavior of the rational
programmer (and real programmers, too).

>>>>

The {\em first challenge\/} concerns the differences among the blame assignment
of the three semantic variants.  While Natural assigns blame to {\em one\/}
component, Transient assigns blame to a sequence of components. The Erasure
semantics does not blame a component {\it per se\/}, but it comes with an
exception location and a stack trace, which implicitly suggests parties to
blame.  The different strategies greatly affect the behavior of the rational
programmer (and real programmers, too).

The {\em second challenge\/} is to find a representative collection of
impedance mismatches. They must represent mistakes that programmers
accidentally create and that the run-time checks of academic systems catch. In
other words, the experiment calls for a collection of type mistakes in
mix-typed programs that is representative of those ``in the wild.''
Unfortunately no such collection exists, and with good reason. The kind of
mistakes needed are typically detected by unit or integration tests; even if it
takes some time to find their sources, these mistakes do not make it into code
repositories with appropriate commit messages.

@@

### 2021-03-01 writing/mutate-benchmarks.tex
re-established the old organization

>>>>

The definition of interesting debugging scenarios creates a powerful filter. All
together, the listed mutators produce 16,800 mutants with at least one
interesting debugging scenario across all benchmarks.  Broken down by benchmark,
the mutators produce at least 40 interesting scenarios for every benchmark, and
these scenarios originate from at least four different mutators per benchmark.
Thus, the mutators result in a sizable and diverse population of scenarios for
every benchmark.  Furthermore, every mutator contributes scenarios to at least
one benchmark.  Some mutators apply only to a few benchmarks, because they
target rather specific features; for instance, the class-focused mutators are
mainly effective in a program that makes extensive use of object-oriented
features.

### 2021-03-01 writing/rational-experiment.tex
re-established the old organization

Furthermore, our experiment can compare the relative usefulness of blame
between any two of the three semantics. 
\begin{itemize}
\item[$Q_*$] Is blame for X more useful than blame for Y? (Where X and Y are any of Natural, Transient, or Erasure)
\end{itemize}

@@

In detail we answer $Q_1$  by comparing the success of the 
Natural blame and Natural exception trails for all interesting 
debugging scenarios from section~\ref{sec:mutate}.
  The first step is to construct each
mutant's scenario lattice and identify their interesting debugging
scenarios.
Our test
bed extends the trails that start from such roots according to the Natural-blame programmer.  If no scenarios
can be added to the trail, we check if
the last scenario of the trail type-checks or not. If it does, we record that the Natural-blame
trail is successful, and otherwise that it fails. We repeat the process for the
same roots again but for the other mode, Natural exceptions.
 Figure~\ref{fig:process}
summarizes this
experimental process for one mode of the rational programmer and connects
it with the mutations from section~\ref{sec:mutate}.
After completing the experiment, we calculate the
success/failure results of the trails to determine for each root whether Natural blame
is more useful than Natural exceptions. We
obtain a positive answer for
$Q_1$ when a root exists where the above is true since it is evidence that
there is at least one interesting scenario that the rational programmer
manages to debug because of blame. 
The process is analogous for $Q_2$ and $Q_3$, employing the respective
modes of the rational programmer.

>>>>

Furthermore, the experiment allows a comparison of the relative usefulness of blame
information:
\begin{itemize}
\item[$Q_*$] Is blame for X more useful than blame for Y (for X, Y in Natural, Transient, or Erasure)?
\end{itemize}

@@

In detail the answer to $Q_1$ demands a comparison of the success of the 
Natural blame and Natural exception trails for all interesting 
debugging scenarios.
  The first step is to construct each
mutant's scenario lattice and identify their interesting debugging
scenarios.
Our test
bed extends the trails that start from such roots according to the Natural-blame programmer.  If no scenarios
can be added to the trail, we check if
the last scenario of the trail type-checks or not. If it does, we record that the Natural-blame
trail is successful, and otherwise that it fails. We repeat the process for the
same roots again but for the other mode, Natural exceptions.
 Figure~\ref{fig:process}
summarizes this
experimental process for one mode of the rational programmer and connects
it with the mutations from section~\ref{sec:mutate}.
After completing the experiment, we calculate the
success/failure results of the trails to determine for each root whether Natural blame
is more useful than Natural exceptions. We
obtain a positive answer for
$Q_1$ when a root exists where the above is true since it is evidence that
there is at least one interesting scenario that the rational programmer
manages to debug with blame information. 
The process is analogous for $Q_2$ and $Q_3$, using the respective
modes of the rational programmer.

### 2021-03-01 writing/results.tex
re-established the old organization

\input{mutate-benchmarks-figure.tex}
\sub{benchmarks} {Which Software to Use As Benchmarks}

\subsection{XXX}
We run the experimental process from section~\ref{sec:rational} on the
sampled debugging scenarios from section~\ref{sec:sample} using a machine with two Intel Xeon Gold 6258R processors (28 doubly-threaded cores each) and 500GB of memory.
Each debugging scenario had a timeout limit of 4 minutes and a
memory limit of 6GB. The complete experiment required
over 30,000 hours of compute hours.

\begin{wrapfigure}{r}{.40\textwidth}
  \centering
  \includegraphics[width=0.40\textwidth]{./plots/success-bars}
  \caption{Success baselines: The estimated percentage of scenarios for which each mode succeeds in locating the bug.
  }
  \label{fig:success-bars}
\end{wrapfigure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}
  \caption{Usefulness comparisons: Each plot depicts a head-to-head comparison of the entitled mode against every other mode.
  The portion above 0 (in green) is the estimated percentage of scenarios where the entitled mode is more useful than each of the other modes.
  The portion below 0 (in red) is the estimated percentage of scenarios with the inverse situation.
  The upper bound of error margin is 0.02\%.}
  \label{fig:avo-bars}
\end{figure}

@@

  \caption{Blame usefulness analysis: Each diagram shows the breakdown of how three modes' successful scenarios overlap.
  The percentage of scenarios covered by each circle are proportions for which the corresponding mode succeeds.
  For example, in the breakdown of Natural, all three modes succeed on the same scenario 57.3\% of the time, only Natural and Natural exceptions succeed on 29.1\% of the scenarios, only Natural and Erasure succeed on 2.1\%, and Natural alone succeeds on 9\%.
  }
  \label{fig:success-venns}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=0.8\textwidth]{./plots/bt-lengths-table}
  \caption{Programmer effort: Each plot depicts the distribution of trail
  lengths for a given mode across all benchmarks.}
  \label{fig:effort-table}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=0.9\textwidth]{./plots/bt-length-comparisons}
  \caption{Effort comparisons: Each plot depicts the distribution of scenarios with trail length differences ranging from -3 to 3.
  A negative difference means that the first mode's trail is three steps shorter than the second mode's trail for the same scenario, and a positive difference is the reverse.
  Only scenarios where both modes succeed are considered.
  The 10|85 on the y-axis indicates that the axis is truncated between 10 and 85\%.}
  \label{fig:effort-comparisons}
\end{figure}

>>>>

%% -----------------------------------------------------------------------------

We run the experimental process from section~\ref{sec:rational} on the
sampled debugging scenarios from section~\ref{sec:sample} using a machine with two Intel Xeon Gold 6258R processors (28 doubly-threaded cores each) and 500GB of memory.
Each debugging scenario had a timeout limit of 4 minutes and a
memory limit of 6GB. The complete experiment required
over 30,000 hours of compute hours.

\begin{wrapfigure}{r}{.40\textwidth}
  \centering
  \includegraphics[width=0.40\textwidth]{./plots/success-bars}
  \caption{Success baselines: The estimated percentage of scenarios for which each mode succeeds in locating the bug.
  The upper bound of error margin is 0.02\%.
  }
  \label{fig:success-bars}
\end{wrapfigure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{./plots/avo-bars}
  \caption{Usefulness comparisons: Each plot depicts a head-to-head comparison of the entitled mode against every other mode.
  The portion above 0 (in green) is the estimated percentage of scenarios where the entitled mode is more useful than each of the other modes.
  The portion below 0 (in red) is the estimated percentage of scenarios with the inverse situation.
  The upper bound of error margin is 0.02\%.
  }
  \label{fig:avo-bars}
\end{figure}

@@

  \caption{Blame usefulness analysis: Each diagram shows the breakdown of how three modes' successful scenarios overlap.
  The percentage of scenarios covered by each circle are proportions for which the corresponding mode succeeds.
  For example, in the breakdown of Natural, all three modes succeed on the same scenario 57.3\% of the time, only Natural and Natural exceptions succeed on 29.1\% of the scenarios, only Natural and Erasure succeed on 2.1\%, and Natural alone succeeds on 9\%.
  The upper bound of error margin is 0.02\%.
  }
  \label{fig:success-venns}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{./plots/bt-lengths-table}
  \caption{Programmer effort: Each plot depicts the distribution of trail
  lengths for a given mode across all benchmarks.}
  \label{fig:effort-table}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{./plots/bt-length-comparisons}
  \caption{Effort comparisons: Each plot depicts the distribution of scenarios with trail length differences ranging from -3 to 3.
  A negative difference means that the first mode's trail is three steps shorter than the second mode's trail for the same scenario, and a positive difference is the reverse.
  Only scenarios where both modes succeed are considered.
  The 10|85 on the y-axis indicates that the axis is truncated between 10 and 85\%.}
  \label{fig:effort-comparisons}
\end{figure}

### 2021-03-01 writing/sample.tex
re-established the old organization

As is, the chosen mutators generate a huge number of debugging scenarios,
approximately 1,000,000 for a suitable benchmark suite such as the one used for
the first experiment (see~sec.~\ref{sub:results-benchmarks}). This number of
scenarios is far too large to even identify the interesting ones among them.
Furthermore this population is heterogeneous; different scenarios come from
different mutants and different mutants are the result of a different mutator
and benchmark pair.

>>>>

As is, the chosen mutators generate a huge number of debugging scenarios,
approximately 1,000,000 for the chosen benchmark. This number of scenarios is
far too large to even identify the interesting ones among them.  Furthermore
this population is heterogeneous; different scenarios come from different
mutants and different mutants are the result of a different mutator and
benchmark pair.
